---
title: 'EpiFusion: Joint inference of the effective
  reproduction number by integrating epidemiological and phylodynamic modelling with
  particle filtering'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code to Fully Reproduce Results {.tabset}

## Main Manuscript
We will be loading the EpiFusion results using the R package `EpiFusionUtilities`, and plotting them using some functions in the `plotting_utilities` script in this repo. To install `EpiFusionUtilities` via devtools you can run this chunk:
```{r install_EpiFusionUtilities} 
devtools::install_github("")
library(EpiFusionUtilities)
```

### Loading Dataset Truths
Throughout the paper, the true value of the infection or R(t) trajectories is used in graphs,

### Figure 1 is a schematic made in powerpoint

### Figure 2

```{r Figure2}
introduction_combined <- extract_posterior_epifusion(load_raw_epifusion("Results/introduction_Combined_300Particles_2000Steps_AnalysisType1_2024-03-27_18-17-34/"))

```

## Supplementary Information

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


